Details of specific functions

### 2021-03-30 inst/gitbook/03_specific-tutorials.Rmd
updated ancestral.dist

#### Centroids, displacements, and ancestral distance metrics {#centroids}

@@

The `ancestral.dist` metric works on a similar principle as the `centroids` function but changes the centroid to be the coordinates of each element's ancestor.
Therefore this functions needs a tree and node coordinates as additional arguments:

```{r}
## A generating a random tree with node labels
tree <- rtree(5) ; tree$node.label <- paste0("n", 1:4)
## Adding the tip and node names to the matrix
dummy_space2 <- dummy_space[-1,]
rownames(dummy_space2) <- c(tree$tip.label, tree$node.label)

## Calculating all the ancestral nodes
all_anc_centroids <- nodes.coordinates(dummy_space2, tree,
                                       full = TRUE)

## Calculating the distances from the ancestral nodes
ancestral_dist <- dispRity(dummy_space2, metric = ancestral.dist,
                           nodes.coords = all_anc_centroids)

>>>>

#### Centroids, displacements and ancestral distances metrics {#centroids}

@@

The `ancestral.dist` metric works on a similar principle as the `centroids` function but changes the centroid to be the coordinates of each element's ancestor (if `to.root = FALSE`; default) or to the root of the tree (`to.root = TRUE`).
Therefore this function needs a matrix that contains tips and nodes and a tree as additional argument.

```{r}
## A generating a random tree with node labels
my_tree <- makeNodeLabel(rtree(5), prefix = "n")
## Adding the tip and node names to the matrix
dummy_space2 <- dummy_space[-1,]
rownames(dummy_space2) <- c(tree$tip.label, tree$node.label)

## Calculating the distances from the ancestral nodes
ancestral_dist <- dispRity(dummy_space2, metric = ancestral.dist,
                           tree = my_tree)
